---
title: "Week7 HW"
author: "Hana"
date: "October 4, 2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Upload file and change name into character
```{r readfile}
df = read.csv("../data/california-state-university-2015.csv")
df$Employee.Name = as.character(df$Employee.Name)
```

### Find all entries with name "Martinez"
```{r allMartinezentries}
my_pattern = "Martinez"
df$Employee.Name[grepl(my_pattern, df$Employee.Name)]
```

### Everyone whose name start with the letter 'Will'*
```{r startwithWil}
my_pattern2 = "^Wil"
df$Employee.Name[grepl(my_pattern2, df$Employee.Name)]
```

### Everyone with a hyphenated name
```{r hyphenatedname}
my_pattern3 = "-"
df$Employee.Name[grepl(my_pattern3, df$Employee.Name)]
```

### Everyone who middle name is Paul
```{r Paulmiddle}
my_pattern4 = "\\sPaul\\s"
df$Employee.Name[grepl(my_pattern4, df$Employee.Name)]
```

### All people with the last name Martinez
```{r Martinezlastname}
my_pattern5 = "Martinez$"
df$Employee.Name[grepl(my_pattern5, df$Employee.Name)]
```

### All people with lastname Martinez (but no hypened name, no Jr.)
```{rMartineznohypen}
my_pattern6 = "[^[:punct:]]Martinez$"
df$Employee.Name[grepl(my_pattern6, df$Employee.Name)]
```

### First name starts with E, has a middle initial, and last name is Martinez
```{r}
my_pattern7 = "^E.*\\s[[:upper:]]\\sMartinez$"
df$Employee.Name[grepl(my_pattern7, df$Employee.Name)]
```

### First name starts with E, has no middle initial, and last name is Martinez

Try thinking of it this way: You need someone with a first name that starts with E, but because it's a first name (not a middle initial), the E should then be followed immediately by at least one more lower case letter. And then you only want that name to be followed by a space + Martinez, not by any other initial or name. So that part of the pattern could be specified in a very straightforward manner by making it just search for a space + Martinez. See if that approach yields some results. 
```{r}
my_pattern8 = "^E.*[[:lower:]]\\sMartinez$"
my_pattern9 = "^\\<E[a-z]*.\\sMartinez$"
df$Employee.Name[grepl(my_pattern8, df$Employee.Name)]
df$Employee.Name[grepl(my_pattern9, df$Employee.Name)]
```

