---
title: "Base Salary for Registered Nurse"
author: "Hana"
date: "September 19, 2017"
output: word_document
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE, fig.align = 'center')
```

## Setting the work directory
I set the working directory to upload the file 

```{r workingdir, echo= TRUE}
# setwd("C:/Users/Hana/255E")
```

### Upload the file
I uploaded the CSV file from the file directory

```{r fileupload, echo=TRUE}
df = read.csv("../data/california-state-university-2015.csv")
```

## Set different levels for job title
I set up the different level of job title so I can easily find "Registered Nurse"

```{r joblevel, echo= TRUE}
levels(df$Job.Title)
```

### Registered Nurse I
I pulled out the column that contains "Registered Nurse I" and all of the row associate with it.

```{r RNI, echo= TRUE}
RNI = df[df$Job.Title == "REGISTERED NURSE I", ]
```

### Registered Nurse II
I pulled out the column that contains "Registered Nurse II" and all of the row associate with it.

```{r RNII, echo= TRUE}
RNII = df[df$Job.Title == "REGISTERED NURSE II", ]
```

### Registered Nurse III
I pulled out the column that contains "Registered Nurse III" and all of the row associate with it.

```{r RNIII, echo= TRUE}
RNIII = df[df$Job.Title == "REGISTERED NURSE III", ]
```

## Merging the data sets
Since RNI, RNII and RNIII had the same column and fifferent row, I combined them into RNall.

```{r bind, echo= TRUE}
RNall = rbind(RNI, RNII, RNIII)
```

### Drop other levels
Since RNall contain other job level, I dropped the unnecessary one, and only keep RNI, RNII and RNIII

```{r droplevel, echo= TRUE}
RNall = droplevels(RNall)
```

## Box plot
I created a box plot to show the base salary of 3 different level of registered nurse- RNI, RNII and RNIII.

```{r boxplot, echo= TRUE, fig.cap="Base Salary for Registered Nurse"}
boxplot(Base.Pay~Job.Title,
        data = RNall, xlab = 'Job Title', ylab = 'Base Salary',
        col = c("aquamarine", "turquoise", "palegreen2"),
        main = "Base Salary for Registered Nurse")
```

## Average bease pay 
I calculated the average base pay for each level of registered nurse

```{r aggregate, echo= TRUE}
mean_salary= aggregate(Base.Pay~Job.Title,
          data = RNall, FUN = mean)
mean_salary
```

### Formating table out of the data frame
I used the 'kable' function to make a nicely formatted table out of the data frame

```{r meantable, echo= TRUE, results='asis'}
kable(mean_salary, caption = 'Average Base Pay for Registered Nurse')
```







